Bird beak's elaboration and exploration

### 2022-10-17 Analysis/02-mcmcmcglmmm_analysis.Rmd
Update 02-mcmcmcglmmm_analysis.Rmd

## Running the three MCMCglmm models
100k_params_shapespace_8D_31levels <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(param_chains, file = "../Data/Processed/MCMCglmm/100k_params_shapespace_8D_31levels_chain1.rda")
```

@@

```{r, get_model_parameters, eval = FALSE}
## Load the computed models
param_chains <- list()
for(i in 1:3) {
    load(paste0("../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/shapespace_allbirds_lvl_superorder_order_param", i, ".rda"))
    param_chains[[i]] <- shapespace_allbirds_lvl_superorder_order_param[[1]]
}
## Extract the parameters from the parameter chains
est_params <- extract.parameters(param_chains)
```

@@

The chains are then run on the cluster
TODO: details

@@

@@

## Passeriformes focus

>>>>

## Running the three MCMCglmm models
params_shapespace_8D_32levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(param_chains, file = "../Data/Processed/MCMCglmm/params_shapespace_8D_32levels_20k_chain1.rda")
```

@@

```{r, get_model_parameters, eval = FALSE}
## Load the computed models
param_chains <- list()
for(i in 1:3) {
    load(paste0("../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k_chain", i, ".rda"))
    param_chains[[i]] <- params_shapespace_8D_32levels_20k[[1]]
}
## Extract the parameters from the parameter chains
est_params <- extract.parameters(param_chains)
```

@@

The chains are then run on the cluster for 400 replicates.

```{r, eval = FALSE}
## Don't run:
run.mini.chains(shapespace_allbirds_lvl_superorder_order, replicates = 400)
```

Note that the previous line is running the 400 replicates in a serial way, it is much more efficient to run each one separately in parallel across 400 CPUs.
Each individual replicate runs for around 50 hours on a 2.4Ghz CPU and requires around 9GB of RAM.
The whole process was completed in around 2 CPU years.

@@

The following script was used to combine the 400 mini chains into the combined chain used for further analysis.
Note that this script is relying on relative paths that might need to be set up before running and are probably dependent on different clusters' architectures.

@@

# Passeriformes focus

The following section repeats every step as highlighted above but applied to the passeriformes as a subset of the entire dataset.
